### 2014-01-15 Docs/visualization/visualization.tex
fix copy-paste error for omegadot
some yt cleaning

{\tt omegadot(*)}      & $(\rho X_k)/\rho$ & {\tt plot\_omegadot} \\

@@

%-----------------------------------------------------------------------------
% yt
%-----------------------------------------------------------------------------
\section{Visualizing with \yt}
\yt is a Python package for analyzing and visualizing simulation data.
Originally \yt was written for the {\tt Enzo} code, with focus on
cosmological simulation data.  It has since been refactored to remove
the specific {\tt Enzo}isms, and now can work on various data formats,
such as the BoxLib data from \maestro\ and \castro, HDF5 data
from {\tt FLASH}, and data from the SPH code {\tt Gadget}.  For more
information, see the \yt homepage at {\tt http://yt.enzotools.org/}.

\subsection{Installing \yt}
The easiest way to obtain \yt is through the use of an installation script:
\begin{lstlisting}[language=bash,mathescape=false]
> wget http://hg.enzotools.org/yt/raw-file/stable/doc/install_script.sh
> bash install_script.sh
\end{lstlisting}
By default, this \yt install script will download and install, in its
own isolated environment, all the secondary utilities needed to get \yt
up and running.  Note that this currently includes installing {\it
  hdf5 1.6.9, zlib 1.2.3, bzip2 1.0.5, libpng 1.2.43, freetype 2.4.4,
  Python 2.6.3, numpy 1.5.1, matplotlib 1.0.0, mercurial 1.7.1,
  ipython 0.10, h5py 1.2.0, Cython 0.14, Forthon 0.8.4} as well as a
\yt {\it mercurial} bundle of changes.  You can turn off the automatic
installation of any of these particular packages by setting the
appropriate {\tt INST\_}* variable to zero in the install script;
you may have to then change some of *{\tt \_DIR} variables to point to
your own particular installation of that package.  I usually just let
\yt install its own stuff, which ensures things are working properly.

After the install script has finished, and assuming you let \yt install its own packages, you'll need to {\it prepend} some environment variables with \yt locations so that your system finds those first and stops looking.  For example, the \yt specific information in my {\tt .bashrc} file looks like this
\begin{lstlisting}[language=bash,mathescape=false]
# yt stuff
export YT_DEST=~/install/yt/current/yt-x86_64
export PATH=${YT_DEST}/bin/:$PATH
export PYTHONPATH=${YT_DEST}/lib/python2.6/site-packages/:$PYTHONPATH
export LD_LIBRARY_PATH=${YT_DEST}/lib/:$LD_LIBRARY_PATH
\end{lstlisting}
where I have {\tt ~/install/yt/current} as a soft link to my \yt
installation directory.

>>>>

{\tt omegadot(*)}      & $\dot{\omega}_k$ & {\tt plot\_omegadot} \\

@@

%-----------------------------------------------------------------------------
% yt
%-----------------------------------------------------------------------------
\section{Visualizing with \yt}
\yt is a Python package for analyzing and visualizing simulation data.
Originally \yt was written for the {\tt Enzo} code, with focus on
cosmological simulation data.  It has since been refactored to remove
the specific {\tt Enzo}isms, and now can work on various data formats,
such as the BoxLib data from \maestro\ and \castro, HDF5 data
from {\tt FLASH}, and data from the SPH code {\tt Gadget}.  For more
information, see the \yt homepage at \url{http://yt-project.org/} and
\cite{yt}.

\noindent {\bf Note: for \maestro\ data, you need to use \yt 3.0 or later.}

\subsection{Installing \yt}
The easiest way to obtain \yt is through the use of an installation script:
\begin{lstlisting}[language=bash,mathescape=false]
> wget http://hg.enzotools.org/yt/raw-file/stable/doc/install_script.sh
> bash install_script.sh
\end{lstlisting}
By default, this \yt install script will download and install, in its
own isolated environment, all the secondary utilities needed to get
\yt up and running.  Note that this currently includes installing {\it
  hdf5, zlib, bzip2, libpng, freetype, python, numpy, matplotlib,
  mercurial, ipython, h5py, Cython, Forthon} as well as a \yt {\it
  mercurial} bundle of changes.  You can turn off the automatic
installation of any of these particular packages by setting the
appropriate {\tt INST\_}* variable to zero in the install script; you
may have to then change some of *{\tt \_DIR} variables to point to
your own particular installation of that package.  It is usually best
to just let \yt install its own stuff, which ensures things are
working properly.

After the install script has finished, and assuming you let \yt
install its own packages, you'll need to {\it prepend} some
environment variables with \yt locations so that your system finds
those first and stops looking.  \yt provides a simple script to
do this, which will be announced upon successful completion.

%% \begin{lstlisting}[language=bash,mathescape=false]
%% # yt stuff
%% export YT_DEST=~/install/yt/current/yt-x86_64
%% export PATH=${YT_DEST}/bin/:$PATH
%% export PYTHONPATH=${YT_DEST}/lib/python2.6/site-packages/:$PYTHONPATH
%% export LD_LIBRARY_PATH=${YT_DEST}/lib/:$LD_LIBRARY_PATH
%% \end{lstlisting}
%% where I have {\tt ~/install/yt/current} as a soft link to my \yt
%% installation directory.
